SPARQL on the open, decentralised Web

### 2016-06-05 dissertation/motivation.tex
Minor

It is crucial, however, that we note that the Internet infrastructure
is accommodating for solving parts of this problem with the presence
of caches at several different levels. We would need to create an
infrastructure to take advantage of these caches, and encourage data
publishers to include metadata to allow caches to be managed in a
standard-defined way. The scale at which this can already be done was
at first important to understand.

>>>>

We therefore proceed with the understanding that the Internet
infrastructure is accommodating for solving parts of this problem with
the presence of caches at several different levels. We would need to
create an infrastructure to take advantage of these caches, and
encourage data publishers to include metadata to allow caches to be
managed in a standard-defined way. The scale at which this can already
be done was at first important to understand.
